Temporal stability in human interaction networks: sector sizes, topological prominence and activity along different timescales (Supporting Information document)

### 2015-10-17 supportingInformation.tex
arrumado titulo do supporting information

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and time activity (Supporting Information document)}% Force line breaks with \\

>>>>

\title[Interaction networks stability (Supporting Information)]{Temporal stability in human interaction networks: sector sizes, topological prominence and activity along different timescales (Supporting Information document)}% Force line breaks with \\
